%header
\documentclass{resume} % Use the custom resume.cls style
\usepackage{paralist}
%\usepackage{hyperref}
\usepackage{graphicx}

\usepackage[left=0.75in,top=1.25in,right=0.75in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Jonathan Wilding} % Your name

\address{jonathan.wilding@hcl.com $\diamond\;$ (385)482-5644 }%\\} % 
\address{ linkedin.com/in/j-wilding $\diamond\;$ github.com/j-wilding }
\begin{document}
\\~\\

%education
\begin{rSection}{Education}
{\bf B.S., Mathematics }\hfill {Apr. 2018 - Apr. 2021} \\
\textit{Brigham Young University, Provo, UT}
\begin{itemize}
    \item Software Engineering Emphasis
\end{itemize}
\end{rSection}

%skills
\begin{rSection}{Skills}
    \textbf{Highly Proficient}\\
        \begin{tabular}{ l l l l l l }
            AZ 900 Azure Cloud & Azure Data Lake & Data Factory & Databricks & Linear Algebra & SQL \\
            Python & Pandas & Linux & Git & Data Structures  
        \end{tabular}\\\\
    \textbf{Proficient}\\
        \begin{tabular}{ l l l l l l l }
            AWS Cloud & Snowflake & Data Warehousing & Cloud & Big Data & Data Modeling & NumPy \\
            Spark & MongoDB & JavaScript & HTML5 & Vue.js &  Tailwindcss & CSS
        \end{tabular}
\end{rSection}

\begin{rSection}{Experience}
    \textbf{Junior Developer}\hfill{Oct. 2021 - Present}\\
    \textit{HCL Technologies, Sacramento, CA} 
    \begin{itemize}
        %\setlength\itemsep{0em}
        \item Orchestrated data pipeline to automate ETL of customer data in Azure Data Factory.
            \begin{itemize}
                \item Refined raw CSV customer data into cleansed and transformed columnar
                    datasets, in a three tiered Delta Lake architecture, with Bronze, Silver and
                    Gold tiered datasets.
                \item The Bronze tables moved data into Azure Data Lake Storage Gen 2 and
                    converted CSV to Parquet format for efficiency.
                \item Silver Level contained the validated and transformed data of five separate
                    tables. Used conditional expressions and table lookups to log and filter
                    errors and invalid data entries.
                \item The Gold tier table was created as an aggregate table by a series of queries
                    and joins, to produce an ultra-refined table for analytics and machine
                    learning.
            \end{itemize}
        \item Generated dashboard of key performance indicators for customer data with Python in
            Databricks.
            \begin{itemize}
                \item Wrote complex SQL queries to compile eight key performance indicators, and
                    created over a dozen visualizations to communicate the story behind the data.
                    Improved overall stakeholder understanding of the customer data.
            \end{itemize}
        \item Predicted customer churn in Python using Pandas and Sklearn with a logistic
            regression model trained to oversample the minority class with SMOTE. 
            \begin{itemize}
                \item Compared the performance of training data with and without oversampling
                    the minority class. 
                \item Assessed that by aggressively predicting customer churn, we can target the 
                    customers which are more likely to churn with retention programs.
                \item Identified the features with the most significant coefficients in the
                    churn model to direct potential retention programs.
            \end{itemize}

    \end{itemize}
    \textbf{Web Development - Research Assistant}\hfill{ Sep.  2020 - May 2021}\\
    \textit{Information Systems Dept., Brigham Young University, Provo, UT} 
    \begin{itemize}
        %\setlength\itemsep{0em}
        \item Designed and produced a web application to test and analyze participant interruptive
            multitasking performance with A/B testing.
        \item Developed a full-stack, multiple-choice form creation and management system with
            Vue.js, Express.js and MongoDB.
    \end{itemize}
\textbf{Machine Learning Support - Research Assistant} \hfill{Oct. 2019
- Jun. 2020}\\
\textit{Mechanical Engineering Dept., Brigham Young University, Provo, UT}
    \begin{itemize}
        \item Reduced run time by hours and enabled ML models to run remotely by centralizing
            computational resources to our high-performance server using JupyterHub and web
            protocols.
    \end{itemize}
\textbf{Mongolian Teacher} \hfill {Sep. 2018 - Sep. 2019}\\
\textit{Missionary Training Center, Provo, UT} 
    \begin{itemize}
        \item Taught Mongolian to groups of 6-10 missionaries in an immersive 10-week language
            course.
        \item Improved efficiency in planning by creating a website to centralize teaching
            resources and materials.
    \end{itemize}
\textbf{Product Quality Control and Regulatory Teammate}    \hfill {Jan. 2018 -
Apr. 2018}\\
\textit{Golub Corporation, Schenectady, NY}                 \hfill {Jan. 2015 -
Dec. 2015}  
    \begin{itemize}
        \item Automated nutrition label verification with a JavaScript web application for product
            category managers, saving roughly 30 seconds for each label while improving accuracy.
        \item Transformed data entry in Excel from a 2-minute process to 15 seconds, with
            VBA scripting.
    \end{itemize}
\end{rSection}

\end{document}
