%header
\documentclass{resume} % Use the custom resume.cls style
\usepackage{paralist}
\usepackage{hyperref}

\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Jonathan Wilding} % Your name

\address{jonathan.r.wilding@gmail.com $\diamond\;$ (385)482-5644 }%\\} % 
\address{
\href{https://www.linkedin.com/in/j-wilding}{linkedin.com/in/j-wilding} $\diamond\;$
\href{https://www.github.com/j-wilding}{github.com/j-wilding}}
\begin{document}

%education
\begin{rSection}{Education}
{\bf B.S., Mathematics }\hfill {Apr. 2018 - Apr. 2021} \\
\textit{Brigham Young University, Provo, UT}
\begin{itemize}
    \item Data Science Emphasis
\end{itemize}
\end{rSection}

%skills
\begin{rSection}{Skills}
    \textbf{Highly Proficient}\\
        \begin{tabular}{ l l l l l l }
            Azure Data Lake & Data Factory & Databricks & Linear Algebra & SQL \\
            Python & Pandas & Linux & Git & Data Structures  
        \end{tabular}\\\\
    \textbf{Proficient}\\
        \begin{tabular}{ l l l l l l }
            Data Warehousing & Cloud & Big Data & Data Modeling & NumPy & PySpark \\
            MongoDB & JavaScript & HTML5 & Vue.js &  Tailwindcss & CSS
        \end{tabular}
\end{rSection}

\begin{rSection}{Experience}
    \textbf{Junior Developer}\hfill{Oct. 2021 - Present}\\
    \textit{HCL Technologies, Sacramento, CA} 
    \begin{itemize}
        %\setlength\itemsep{0em}
        \item Orchestrated data pipeline to automate ETL of customer data in Azure Data Factory.
        \item Generated dashboard of key performance indicators for customer data with Python in
            Databricks.
    \end{itemize}
    \textbf{Web Development - Research Assistant}\hfill{ Sep.  2020 - May 2021}\\
    \textit{Information Systems Dept., Brigham Young University, Provo, UT} 
    \begin{itemize}
        %\setlength\itemsep{0em}
        \item Designed and produced a web application to test and analyze participant interruptive
            multitasking performance with A/B testing.
        \item Developed a full-stack, multiple-choice form creation and management system with
            Vue.js, Express.js and MongoDB.
    \end{itemize}
\textbf{Machine Learning Support - Research Assistant} \hfill{Oct. 2019
- Jun. 2020}\\
\textit{Mechanical Engineering Dept., Brigham Young University, Provo, UT}
    \begin{itemize}
        \item Reduced run time by hours and enabled ML models to run remotely by centralizing
            computational resources to our high-performance server using JupyterHub and web
            protocols.
    \end{itemize}
\textbf{Mongolian Teacher} \hfill {Sep. 2018 - Sep. 2019}\\
\textit{Missionary Training Center, Provo, UT} 
    \begin{itemize}
        \item Taught Mongolian to groups of 6-10 missionaries in an immersive 10-week language
            course.
        \item Improved efficiency in planning by creating a website to centralize teaching
            resources and materials.
    \end{itemize}
\textbf{Product Quality Control and Regulatory Teammate}    \hfill {Jan. 2018 -
Apr. 2018}\\
\textit{Golub Corporation, Schenectady, NY}                 \hfill {Jan. 2015 -
Dec. 2015}  
    \begin{itemize}
        \item Automated nutrition label verification with a JavaScript web application for product
            category managers, saving roughly 30 seconds for each label while improving accuracy.
        \item Transformed data entry in Excel from a 2-minute process to 15 seconds, with
            VBA scripting.
    \end{itemize}
\end{rSection}

\end{document}
