%header
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Jonathan Wilding} % Your name

\address{jonathan.r.wilding@gmail.com \\ (385)482-5644 \\
linkedin.com/in/jonathan-wilding}

\begin{document}

%education
\begin{rSection}{Education}

    {\bf B.S., Mathematics }\hfill {Apr. 2021} \\
\textit{Brigham Young University, Provo, UT}
    \begin{itemize}
        \item Computer Science Emphasis
        \item Lucid Software U of U and BYU Programming Competition      \hfill {Oct. 2019}
        \item 4th Place Google Tech Challenge \hfill {Feb. 2020}
        \item Relevant Coursework:
        \item[]
            \begin{tabular}{l l}
                Data Structures & Discrete Mathematics   \\ 
                Mathematical Programming & Computation and Optimization 
            \end{tabular}
    \end{itemize}
\end{rSection}

%skills
\begin{rSection}{Skills}
    \begin{itemize}
        \item Proficient in:
        \item[]
        \begin{tabular}{ l l l }
	Python     & SQL    & Bash \\
 	HTML 	      & CSS    & JavaScript \\
            SSH         & Unix   & Data Structures  \\
            C++        & Vim    & \LaTeX  \\
            Matplotlib & NumPy & Scipy \\
            Gradient Descent & Numerical Linear Algebra  & Singular Value Decomposition
        \end{tabular}
    \end{itemize}
\end{rSection}

\begin{rSection}{Experience}
\textbf{Materials Science Machine Learning Research Assistant} \hfill{Oct. 2019
- Jun. 2020}\\
\textit{Mechanical Engineering Dept., Brigham Young University, Provo, UT}
    \begin{itemize}
        % \item Uses python to generate and compare SOAP vectors (Smooth Overlap of
        % Atomic Positions) in order to increase computing efficiency.  
        \item Configured and maintained Jupyterhub/Apache server for a team of
            several data scientists
        \item Created Bash and Python scripts to automate supercomputing jobs
    \end{itemize}
\textbf{Mongolian Teacher} \hfill {Sep. 2018 - Sep. 2019}\\
\textit{Missionary Training Center, Provo, UT} 
    \begin{itemize}
        \item Created and maintained a website for the area to simplify and
            centralize resources and materials
        \item Increased focus on student success by leading weekly meetings
    \end{itemize}
\textbf{Product Quality Control and Regulatory Teammate}    \hfill {Jan. 2018 -
Apr. 2018}\\
\textit{Golub Corporation, Schenectady, NY}                 \hfill {Jan. 2015 -
Dec. 2015}  
    \begin{itemize}
        \item Built JavaScript web application for managers 
        \item Increased efficiency over 300\% using Microsoft VBA
    \end{itemize}
\end{rSection}

%Projects
\begin{rSection}{Projects}
\textbf{Regex} \hfill{Feb. 2020}
    \begin{itemize}
        \item Organized over 1000 unstructured personnel records into a
            dictionary with regex and python
    \end{itemize}
%\textbf{Linux} \hfill{Feb. 2020}
%    \begin{itemize}
%        \item Configured and personalized Linux desktop environment with Bash scripts
%            and automation
%    \end{itemize}
\end{rSection}

%Relevant experience

\end{document}
